\documentclass[a4paper,12pt]{letter}
%\usepackage{fancyhdr}
\usepackage{hyperref}

%\usepackage[showframe]{geometry}
%\usepackage{layout}

%\usepackage{fullpage}
%\usepackage[T1]{fontenc}
%\usepackage{setspace}

%\usepackage[scaled=0.92]{helvet}
%\usepackage{helvet}
\linespread{1.5}
\address{1500 North Kuhn Drive \\ Palmer, Alaska  99645}
\usepackage{fullpage}
\begin{document}
\begin{letter}{}
\opening{Dear Sir or Madam,}
I write to express my interest in the Data Scientist position currently advertised by The Climate Corporation. I am a mathematician and resident of St Louis. 

I completed my PhD in pure mathematics at the Center for Mathematical Sciences at the University of Cambridge. After completing my PhD degree I started an applied mathematics project with researchers at the Institut National de la Sant\a'e et de la Recherche M\a'edicale (ISERN) in the University of Strasbourg, France, which uses natural language processing, cluster analysis, and machine learning techniques for automated patient diagnosis. I am confident that I have the necessary background in statistics and programming, and the research experience to be able to collect, clean, interpret, and analyze data rigorously. Furthermore, my training as a mathematical researcher enables me to readily acquire working knowledge of new areas with precision and efficiency.

As an academic, I have lectured classes, created interdisciplinary seminars, and given numerous talks at international conferences. I find this to be strong evidence of my ability to present and report results to both members of my area and those outside of it. I pride myself in being a good communicator, and consider it to be one of my vocations.

 I have recently moved to St Louis with my wife and family, where I have immersed myself in our community, spending the past two years exploring the area, making new friends, volunteering for various projects. Thank you for your consideration.

Yours faithfully,

Guilherme Lima 
\end{letter}

\end{document}
 